Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-17 cloneoverflow-latex/cloneoverflow.tex
Updated according to Jens’s comments (haven’t worked on RQ1 though).

\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

While research has mostly focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.

To fill this gap, this paper makes the following  primary contributions:

@@

The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}. Simian with the default configuration ($S_D$) report clones in 1,086 snippets, approximately 1\% of the 144,075 Stack Overflow snippets. Simian with the EvaClone configuration ($S_E$) report 1,531 snippets containing clones. NiCad with the default configuration ($N_D$) reports clones in 1,392 Stack Overflow code snippets. NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,886 cloned snippets mainly due to its relaxed configurations. In terms of the number of clone pairs, $S_D$ reports 67,570 clone pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report a larger clone pair amount of 63,635,844 and 251,449,849 pairs respectively. This is expected since EvaClone configurations prefer recall~\cite{Wang2013}. 
%Using $S_D$, we found 62 clones in average originating from a single Stack Overflow snippet. 62 and 455 respectively. On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average. 
The average clone size reported by $S_D$ is 9.11 lines which is bigger than $S_E$ (5.95 lines). Similarly, $N_D$ has an average clone size of 10.85 lines which is bigger than 6.28 lines reported by $N_E$. We can see from the statistics that EvaClone tunes the tools to report smaller clones. The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\% accordingly. A quick manual check of Simian's clone report revealed that there were 11 problematic snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

As displayed in \Cref{t_agreed_good_clone_pairs}, after we applied clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729. %The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively. The total number of clone candidates is 32,039 pairs. 
We explain them in more details below.

@@

Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria, and therefore are selected for manual classification. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors. $N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
		\hline
		\textit{good} & 18 & 26 & 10 & 2,267 & 2,321 & 2,308 \\
		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 32,560 & 31,729  \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filters} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filters} \\ \cline{3-6}
		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
%		\hline
%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
		\hline
		\multicolumn{7}{l}{*\textit{L}=line $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{R}=reg.~expressions, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
	\end{tabular} %
	%}
\end{table}

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement from the other tool. The disagreement can be from a misalignment of clone lines or totally non-overlapping clones. The disagreed pairs from Simian cover clone pairs in the projects with NiCad's errors (1 projects from $N_D$ and 5 from $N_E$). %that are automatically missing from the agreed clone pairs. 
With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.

Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 632,855 pairs for $N_D$). We applied four filters: \textbf{clone line, regular expression, similarity threshold, and good/ok pairs}. For the clone line filter, we raised the minimum clone size to 10 line since larger clones are more interesting, while smaller ones tend to be false clones~\cite{Saini2016}. Moreover, the study of uniqueness of source code by Gabel and Su~\cite{Gabel2010} suggests that source code are unique when they are larger than seven lines. Since the 10--line threshold is already the default configuration for NiCad, this filter is applied to Simian only (Simian's default configurations has a minimum clone size of 6 lines).~The regular expression filter removes boiler-plate clones of \verb|hashCode()| methods and getters/setters. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity configuration. The last filter, good/ok pairs, removes the clone pairs that have already existed in the agreed clone sets.

@@

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs. The three filters reduced the number of $S_D$ clones to 17,801 pairs. 
%For $N_D$, 10-line threshold is already a minimum NiCad's clone size. However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones. Thus, besides regular expressions and good/ok pair filters, 
We filtered $N_D$ clones by raising the similarity threshold. We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and found that 85\% similarity provided the best balance in terms of the amount of reported clones and feasibility for manual investigation. Using this filter along with the regular expression and the good/ok pair filter, we reduced the size of $N_D$ clones to 88 pairs.

%In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,502 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c|p{8.4cm}}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			IN & Inheritance, interface implementation 
			\\ 
			\hline 
			AC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

We are interested in the analysis of the patterns of online code clones. We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study. Using the $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet. We selected these four criteria so that we could cover the online clones from various aspects. We selected the top 10 from each ranking and obtained 34 unique Stack Overflow snippets. The snippets were associated with 697 clone pairs. Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating. \textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}

The benefit of the study is two-folded. We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs. After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns . The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}. Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow. The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents. Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with an evidence, in the opposite direction to QS. Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones, between Qualitas and Stack Overflow but where we could not find any attribution of copying. %The UD clones are also unique enough to not be a boiler-plate code. 
Pattern ES (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources. Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components. Pattern IN (\textbf{In}heritance/Interface) is cloning by inheritance of the same super class or implementation of the same interface. These two activities usually result in similar overriding methods. The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs. These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements or similar code after normalisation.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

The online clone classification follows the steps depicted in \Cref{fig:classification_process}. First, we look at a pair of clone fragments to see their similarity. If they are accidentally similar clones after code normalisation or false positive clones from the clone detection tools, we classify the pair into AC. If the two fragments are boiler-plate code, the pair is classified into BP. If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN. If the pair is not UD, IN, or AC, we start a detailed investigation. We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying. If an evidence of copying has been found from a Qualitas project, the pair is classified in QS. In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding. On the other hand, if the source code from Qualitas project mentions about copying from Stack Overflow, the pair is classified into SQ. If there is an evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX. Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.

We had in total 31,946 online clone pair candidates for classifications. 2,308 and 11,749 were \textit{good} and \textit{ok} clone pairs respectively. 17,801 and 88 clone pairs are from $S_D$ and $N_D$ after the filtering. Please note that we ignored 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to their large number of clones and the very small average clone sizes of 4.79 and 5.33 lines (see \Cref{tab:raw_stats}). They had high possibilities to be trivial clones.

Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters. As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us captured 28,314 clone pairs and classified them into pattern BP.

There were 3,632 pairs left for the manual check. The first author who has been working on clone detection research for two years took the role of the main investigator performing a manual classification of the 3,632 clone pairs. By consulting the cloning patterns, the main investigator went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair. A relevant and useful observation was also recorded for each clone pair.

@@

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112 online clone pairs with evidences of cloning from Qualitas projects to Stack Overflow. They include 3, 14, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively. Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in Qualitas. The most cloned projects is {\small\texttt{hibernate}} and {\small\texttt{spring}} with 20 clone pairs, followed by {\small\texttt{eclipse}} (15 pairs), and {\small\texttt{hadoop}} (12 pairs). The clones are used as examples and are very similar to their original Qualitas code with limited modifications.

@@

@@

These findings complement a study of clones between software projects~\cite{Svajlenko2014}. We found that the code cloning can also happen among different sources on the Internet just like software projects. There are 30 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html. Both Stack Overflow and {\small\texttt{compiere}} project source code contain attribution to the original source. Another example is a code to generate graphical \textit{Perlin noise}. It is copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/. The code is used in Stack Overflow and {\small\texttt{aoi}} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There other EX clone pairs are from third-party libraries such as {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and the {\small\texttt{bouncycastle}} cryptography project.

@@

%\subsubsection{Outdated Clones}
Outdated code occurs when a piece of code has been copied from its origin to another location and later the original has been updated~\cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}. However, for online code clones, the clones are pervasive and more difficult to detect than in regular software projects due to its large search space and a mix of natural and programming languages combined in the same post. Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the validity of the code snippets. To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.

To search for outdated online code clones, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow and compared them with their latest versions. We downloaded the latest version of the Qualitas projects from their repositories on 26 September 2016. For each QS online clone pair, we use the clone from Qualitas a a proxy. We searched for its latest version by the file name and located the cloned region in the file based on the method name. For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code. We also made sure that the changes did not come from the modifications made to the Stack Overflow snippets by the posters but from the updates in the projects themselves. When we found inconsistent lines between the two versions, we used {\small\texttt{git blame}} to see who modified those lines of code and noted down the timestamps and other details.

>>>>

%\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

While research has mostly focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation. This paper makes the following  primary contributions:

@@

The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}. Simian with the default configuration ($S_D$) reports clones in 1,086 snippets, approximately 1\% of the 144,075 Stack Overflow snippets. Simian with the EvaClone configuration ($S_E$) reports 1,531 snippets containing clones. NiCad with the default configuration ($N_D$) reports clones in 1,392 Stack Overflow code snippets. NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,886 cloned snippets mainly due to its relaxed configurations. In terms of the number of clone pairs, $S_D$ reports 67,570 clone pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report a larger clone pair amount of 63,635,844 and 251,449,849 pairs respectively. This is expected since EvaClone configurations prefer recall~\cite{Wang2013}. 
%Using $S_D$, we found 62 clones in average originating from a single Stack Overflow snippet. 62 and 455 respectively. On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average. 
The average clone size reported by $S_D$ is 9.11 lines which is bigger than $S_E$ (5.95 lines). Similarly, $N_D$ has an average clone size of 10.85 lines which is bigger than 6.28 lines reported by $N_E$. We can see from the statistics that EvaClone tunes the tools to report smaller clones. For the cloned Stack Overflow snippets, the average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\%  respectively. A quick manual check of Simian's clone report revealed that there were 11 problematic snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses. We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors. $N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and \texttt{spring}. We have contacted the creator of NiCad regarding the issues. They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.

As displayed in \Cref{t_agreed_good_clone_pairs}, after we applied clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729. %The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively. The total number of clone candidates is 32,039 pairs. 
We explain them in more detail below.

@@

Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria, and therefore are selected for manual classification. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
Due to NiCad's failures, we do not have NiCad clones from five Qualitas projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Unique \\
		\hline
		\textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
		\hline
	\end{tabular} %
%}
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-6}
		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & & \checkmark & \checkmark & \checkmark & 88 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
%		\hline
%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
		\hline
		\multicolumn{7}{l}{*\textit{L}=line $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{R}=reg.~expressions, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
	\end{tabular} %
	%}
\end{table}

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with the other tool. The disagreement can be from a misalignment of clone lines or totally non-overlapping clones. The disagreed pairs from Simian cover clone pairs in the projects with NiCad's errors (1 projects from $N_D$ and 5 from $N_E$). %that are automatically missing from the agreed clone pairs. 
With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.

Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 632,855 pairs for $N_D$). We applied four filters: \textbf{clone line, regular expression, similarity threshold, and good/ok pairs}. For the clone line filter, we raised the minimum clone size to 10 line since larger clones are more interesting, while smaller ones tend to be false clones~\cite{Saini2016}. Since the 10--line threshold is already the default configuration for NiCad, this filter is applied to Simian only (Simian's default configurations has a minimum clone size of 6 lines).~The regular expression filter removes boiler-plate clones of \verb|hashCode()| methods and getters/setters. The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity configuration. The last filter, good/ok pairs, removes the clone pairs that have already existed in the agreed clone sets. 
% Moreover, the study of uniqueness of source code by Gabel and Su~\cite{Gabel2010} suggests that source code are unique when they are larger than seven lines.

@@

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs. The three filters reduced the number of $S_D$ clones to 17,801 pairs. 
%For $N_D$, 10-line threshold is already a minimum NiCad's clone size. However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones. Thus, besides regular expressions and good/ok pair filters, 
We filtered $N_D$ clones by raising the similarity threshold. We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We tried varying the UPI from 70\% (default -- 632,855 pairs), 80\% (25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that 85\% similarity provided the best balance in terms of the amount of reported clones and feasibility for manual investigation. Using this filter along with the regular expression and the good/ok pair filter, we reduced the size of $N_D$ clones to 88 pairs.

%In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which  classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs). Finally, there are 3,502 pairs remaining which we manually classified them. The classification summary is shown in \Cref{tab:online_clone_classification_results}.

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c|p{8.4cm}}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
			\hline 
			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated \\ 
			\hline 
			IN & Inheritance, interface implementation  \\ 
			\hline 
			AC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

We are interested in the analysis of the patterns of online code clones. We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study. Using the $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet. We selected these four criteria so that we could cover the online clones from various aspects. We selected the top 10 from each ranking and obtained 34 unique Stack Overflow snippets. The snippets were associated with 697 clone pairs. Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.

The benefit of the study is two-folded. We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs. \textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.} After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns . The seven patterns include QS, SQ, EX, UD, BP, IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have evidence to be copied from Qualitas to Stack Overflow. The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents. Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with evidence, in the opposite direction to QS. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.  Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying. %The UD clones are also unique enough to not be a boiler-plate code. 
Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components. Pattern IN (\textbf{In}heritance/Interface) is cloning by inheritance of the same super class or implementation of the same interface. These two activities usually result in similar overriding methods. The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs. These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

The online clone classification follows the steps depicted in \Cref{fig:classification_process}. First, we look at a pair of clone fragments to see their similarity. If they are accidentally similar clones after code normalisation or false positive clones from the clone detection tools, we classify the pair into AC. If the two fragments are boiler-plate code, the pair is classified into BP. If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN. If the pair is not BP, IN, or AC, we start a detailed investigation. We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying. If evidence of copying has been found from a Qualitas project, the pair is classified in QS. In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding. On the other hand, if the source code from the Qualitas project mentions copying from Stack Overflow, the pair is classified into SQ. If there is evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX. Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.

We had in total 31,946 online clone pair candidates for classifications. 2,308 and 11,749 were \textit{good} and \textit{ok} clone pairs respectively. 17,801 and 88 clone pairs are from $S_D$ and $N_D$ after the filtering. Please note that we ignored 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to their large number of clones and the very small average clone sizes of 4.79 and 5.33 lines (see \Cref{tab:raw_stats}). They had a high probability to be trivial clones.

Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters. As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us classified and captured 28,314 clone pairs into pattern BP.

There were 3,632 pairs left for the manual check. The first author who has been working on clone detection research for two years took the role of the main investigator performing a manual classification of the 3,632 clone pairs. By consulting the cloning patterns, the main investigator went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair. %A relevant and useful observation was also recorded for each clone pair.

@@

\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112 online clone pairs with evidences of cloning from Qualitas projects to Stack Overflow. They include 3, 14, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively. Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in a Qualitas project. The most cloned projects are {\small\texttt{hibernate}} and {\small\texttt{spring}} with 20 clone pairs, followed by {\small\texttt{eclipse}} (15 pairs), and {\small\texttt{hadoop}} (12 pairs). The clones are used as examples and are very similar to their original Qualitas code with limited modifications.

@@

These findings complement a study of clones between software projects~\cite{Svajlenko2014}. We found that the code cloning can also happen among different sources on the Internet just like software projects. There are 30 clone pairs that are originated from programming websites. For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html. Both the Stack Overflow and the {\small\texttt{compiere}} project source code contain an attribution to the original source. Another example is a code to generate graphical \textit{Perlin noise}. It is copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/. The code is used in Stack Overflow and {\small\texttt{aoi}} project with attribution. %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license. 
There are other EX clone pairs are from third-party libraries such as {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and the {\small\texttt{bouncycastle}} cryptography project.

@@

@@

%\subsubsection{Outdated Clones}
Outdated code occurs when a piece of code has been copied from its origin to another location and later the original has been updated~\cite{Xia2014}. Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}. However, online code clones are more difficult to detect than in regular software projects due to its large search space and a mix of natural and programming languages combined in the same post. 
%Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the validity of the code snippets. To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.

To search for outdated online code clones, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow and compared them with their latest versions. We downloaded the latest version of the Qualitas projects from their repositories on 26 September 2016. For each QS online clone pair, we use the clone from Qualitas a a proxy. We searched for its latest version by the file name and located the cloned region in the file based on the method name. 
%For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code. We also made sure that the changes did not come from the modifications made to the Stack Overflow snippets by the posters but from the updates in the projects themselves. When we found inconsistent lines between the two versions, we used {\small\texttt{git blame}} to see who modified those lines of code and the timestamps.
